\documentclass[10pt,spanish,9pt,a4]{article}
\usepackage{mathpazo}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[a4paper]{geometry}
\geometry{verbose,lmargin=3cm,rmargin=3cm}
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}
\usepackage{babel}
\addto\shorthandsspanish{\spanishdeactivate{~<>}}

\usepackage{pifont}
\usepackage{url}
\usepackage{amsmath}
\usepackage{setspace}
\setstretch{1.15}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 1},backref=section,colorlinks=false]
 {hyperref}

\makeatletter

\newcommand{\noun}[1]{\textsc{#1}}
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

\newenvironment{c_list}[1]
	{\begin{list}{}
		{\settowidth{\labelwidth}{#1}
		 \setlength{\leftmargin}{\labelwidth}
		 \addtolength{\leftmargin}{\labelsep}
		 \renewcommand{\makelabel}[1]{##1\hfil}}}
	{\end{list}}

\usepackage[framemethod=tikz]{mdframed}

\newmdenv[
  hidealllines=true,
  innerleftmargin=3pt,
  innerrightmargin=3pt,
  leftmargin=-3pt,
  rightmargin=1cm
]{shadedbox}

\AtBeginDocument{
  \def\labelitemi{\Pisymbol{psy}{183}}
  \def\labelitemii{\Pisymbol{psy}{45}}
}

\makeatother

\begin{document}
\pagenumbering{gobble}
\title{\noun{Programming Puzzles}}
\author{Peace Umolu}

\maketitle
\tableofcontents{}

\newpage

\pagenumbering{arabic}

\section{(7 - 19) April 2019}

\subsection{Arya and the Greet War (Easy, Bit Magic)}

The whitewalkers are here and the Great War is on. Each and every
living being is giving their best to save the world from the dead.
Arya fighting with full dedication found that whitewalkers need to
be killed with a pattern or else they wont die. So that she can fight
till the end of the war. She tried to understand the pattern. She
kills every '$Xth$' whitewalker by stabbing them $'N'$ times .
\begin{center}
\begin{tabular}{|r|c|c|c|c|c|c|c|c|c|c|c|}
\hline 
Whitewalker approaching order $(x)$ & 1 & 2 & 3 & $\ldots$ & 55 & $\ldots$ & 98 & $\ldots$ & 101 & $\ldots$ & 198\tabularnewline
\hline 
Number of time-stabbing $(n)$ & 1 & 1 & 2 & $\ldots$ & 5 & $\ldots$ & 3 & $\ldots$ & 4 & $\ldots$ & 4\tabularnewline
\hline 
\end{tabular}
\par\end{center}

This is the hint of the pattern that Arya needs to follow. Help Arya!
\begin{c_list}{0000.0000.0000}
\item [{\textbf{Input}:}] The first line of the input contains an integer
T, denoting the number of test cases. The description of each testcase
follows. Each test case contains a single line with one integer 'X'
the Xth whitewalker .
\item [{\textbf{Output:}}] For each test case in, a new line print the
number of stabs required to kill the 'Xth' whitewalker.
\item [{\textbf{Constraints:}}] $1\leq T\leq200$, $1\leq X\leq200$
\item [{\textbf{Example:}}] \emph{Input} $\left(4,102,95,72,60\right)\implies$\emph{Output}
$\left(4,6,2,4\right)$
\end{c_list}
\textbf{Explanation: }Testcase 1: The number of set bits in the given
number will be the number of stabs required to kill that whitewalker.

Reference \url{https://practice.geeksforgeeks.org/problems/arya-and-the-great-war/0}

\subsection{Rightmost different bit}

Given two numbers $M$ and $N$. The task is to find the position
of rightmost different bit in binary representation of numbers.
\begin{c_list}{0000.0000.0000}
\item [{\textbf{Input}:}] The input line contains T, denoting the number
of testcases. Each testcase follows. First line of each testcase contains
two space separated integers M and N.
\item [{\textbf{Output:}}] For each testcase in new line, print the position
of rightmost different bit in binary representation of numbers. If
both M and N are same then print -1 in this case.
\item [{\textbf{Constraints:}}] $1\leq T\leq100$, $1\leq M\le10^{3}$,
$1\leq N\leq10^{3}$
\item [{\textbf{Example:}}] Input $\left(2,\left(11,9\right),\left(52,4\right)\right)\implies$Output
$\left(2,5\right)$
\end{c_list}
\textbf{Explanation:} Tescase 1: Binary representaion of the given
numbers are: 1011 and 1001, 2nd bit from right is different.

Reference \url{https://practice.geeksforgeeks.org/problems/arya-and-the-great-war/0}
\end{document}
